### 2015-01-08 ASP.tex
CLNS format
mise à jour

In order to develop the nes methods we have used two main frameworks. The first is a logic programming language: the Answer Set Programming (ASP). Precisely it is a logic programming language on which I wrote my bibliographic research report. The second framework is the Process Hitting (PH) a new formalism for the representation of biological regulatory networks. We will see later in this section more details about these two frameworks.

@@

\subsubsection{The syntax and semantic of ASP}
\label{sectionSyntaxeASP}
\begin{enumerate}
\item \textbf{L'alphabet}

@@

Special cases rules \cite{Vladimir, baral2003knowledge} :\\

>>>>

In order to develop these methods we have used two main frameworks. The first is a logic programming language: the Answer Set Programming (ASP), precisely it is a logic programming language. The second framework is the Process Hitting (PH) a new formalism for the representation of biological regulatory networks. We will see later in this section more details about these two frameworks.

@@

\subsubsection{The syntax and semantic of ASP}
\label{sectionSyntaxeASP}
\begin{enumerate}
\item \textbf{The alphabet}

@@

Special cases rules \cite{Vladimir} and \cite{baral2003knowledge} :\\

### 2015-01-08 PH.tex
mise à jour

The concurrent interactions between processes are defined by a set of \emph{actions}.
Actions describe the replacement of a process by another of the same sort
conditioned by the presence of at most one other process in the current state.
An action is denoted by $\PHfrappe{a_i}{b_j}{b_k}$, which is read as
``$a_i$ \emph{hits} $b_j$ to make it \emph{bounce} to $b_k$'',
where $a_i,b_j,b_k$ are processes of sorts $a$ and $b$,
called respectively \emph{hitter}, \emph{target} and
\emph{bounce} of the action.
We also call a \emph{self-hit} any action whose hitter and target sorts are the same,
that is, of the form: $\PHfrappe{a_i}{a_i}{a_k}$.

@@

\begin{definition}[Stable state or fixed point] \\
\label{def:FixPoint1}
Let $PH = (\PHs,\PHl,\PHa)$ be a Process Hitting and
$ \{s_0,..., s_n\} \in \PHl$ be state, $s_n$ is a stable state for $PH$ if and only if $next(s_n) = \emptyset $.
\begin{center}
$s_0 \mapsto s_1 ... \mapsto s_n \mapsto \emptyset $
\end{center}
\end{definition}

\begin{definition}
[Lemme: Stable state or fixed point]
\label{def:FixPoint2}
Let $PH = (\PHs,\PHl,\PHa)$ be a Process Hitting and
$s \in \PHl$ be a state, $s$ is a stable state for $PH$ there is no playable action at the state $s$: 
\begin{center}
$\forall h \in \PHa$, $frappeur(h) ~ \notin s ~ \vee ~ cible(h) \notin s$)
\end{center}
\end{definition}

>>>>

The concurrent interactions between processes are defined by a set of \emph{actions}.
Actions describe the replacement of a process by another of the same sort
conditioned by the presence of at most one other process in the current state.
An action is denoted by $\PHfrappe{a_i}{b_j}{b_k}$, which is read as
"$a_i$ \emph{hits} $b_j$ to make it \emph{bounce} to $b_k$",
where $a_i$, $b_j$, $b_k$ are processes of sorts $a$ and $b$,
called respectively \emph{hitter}, \emph{target} and
\emph{bounce} of the action.
We also call a \emph{self-hit} any action whose hitter and target sorts are the same,
that is, of the form: $\PHfrappe{a_i}{a_i}{a_k}$.

@@

\begin{definition}[Stable state or fix point] \\
\label{def:FixPoint1}
Let $PH = (\PHs,\PHl,\PHa)$ be a Process Hitting and
$ \{s_0,..., s_n\} \in \PHl$ be state, $s_n$ is a stable state for $PH$ if and only if $next(s_n) = \emptyset $.
\begin{center}
$s_0 \mapsto s_1 ... \mapsto s_n \mapsto \emptyset $
\end{center}
\end{definition}

\begin{definition}
[Lemma: Stable state or fix point] \\
\label{def:FixPoint2}
Let $PH = (\PHs,\PHl,\PHa)$ be a Process Hitting and
$s \in \PHl$ be a state, $s$ is a stable state for $PH$ there is no playable action at the state $s$: 
\begin{center}
$\forall h \in \PHa$, $frappeur(h) ~ \notin s ~ \vee ~ cible(h) \notin s$)
\end{center}
\end{definition}

### 2015-01-08 comparaison.tex
mise à jour

\begin{figure}
\label{tab:reachability}
\noindent
\begin{tabular}{|l||c|c|c||c|c|c|c|}
  \hline
   Model& \#procs & \#states & target & Rocca & libddd & GINsim & ASP \\
  \hline
%   & \multicolumn{7}{l|}{Reachability}\\
%  \hline
  tetard \cite{khalis2009smbionet} & 42 & $2^{19}$ & process & 7m17.01s & XX & XX & 0m01.90s \\
  \hline
  ERBB\_G1-S \cite{Samaga2009}  & 152 & $2^{70}$ & state & - &1m55.38s & 2m01.64s & 0m11.84s \\
  \hline
  ERBB\_G1-S & 152 & $2^{70}$ & process & - &1m54.96s & - & 0m05.02s \\
  \hline
  TCRsig40 \cite{Klamt06} & 156 & $2^{73}$ & process & - & out & out & 0m05.02s \\
  \hline
\end{tabular}
\caption{Compared performances of Rocca et al. method, \textsc{libddd}, \textsc{GINsim} and our new method developped in ASP. For each test we find the name of the model, the number of its processes and its states then the target(s). The target can be a network state (set of processes) or one or some processes. "out" marks an execution asking too much time or memory and "-" marks that is not possible to do the test.
}
\end{figure}
\end{center}
This table prensents the comparisons run for 4 dynamic analysis methods applied to examples of biological regulatory networks. The models of these networks where chosen as being representative of different scales, large networks and small networks.
This table shows the effectiveness of our method compared to existing. In fact we develop in the sequel that our method provides more compared to other

@@

We developped new methods for the dynamic properties, 
identifying stable states and finding all possible paths to reach states. Comparing with other methods (Rocca's method, \textsc{GINsim} and \textsc{libddd}) is relatively faster and also permit to edit larger networks (about $2^{73}$ states) but we had also some inconclusif cases. In fact the program is inconclusif if the state is not reachable and there is some loops in the graph so the program may turn indefinitely in one of these loops since it is not possible to achieve the goals or to stop the calculation. We then proposed in this case to limit the increment to a maximum number that can be reached in the case of an endless loop and which may not be in the case where the targets are verified.
\begin{tabbing}
 \texttt{ iClingo find\_path.lp <network\_name>.lp --imax=n}
\end{tabbing}
Should be given some interesting values for this integer $ n $, which sets the maximum number of steps. For example, the total number of states is a maximum (it will never be exceeded by a minimum path). However, it can reduce the number of sorts if it is assumed that one type will be changed by step (which is often the case of Boolean networks) or the number of shares with the same assumption.
Note that if in a way the goal is reached after a time $n$, the calculation stops and displays this path as solution.

>>>>

\begin{figure}
\label{tab:reachability}
\noindent
\begin{tabular}{|l||c|c|c||c|c|c|c|c|}
  \hline
   Model& \#procs & \#states & target & Rocca & Pint & libddd & GINsim & ASP \\
  \hline
  tetard \cite{khalis2009smbionet} & 42 & $2^{19}$ & process & 7m17.01s & \todo{XX} & \todo{XX} & \todo{XX} & 0m01.90s \\
  \hline
  ERBB\_G1-S \cite{Samaga2009}  & 152 & $2^{70}$ & state & - & \todo{XX} &1m55.38s & 2m01.64s & 0m11.84s \\
  \hline
  ERBB\_G1-S & 152 & $2^{70}$ & process & - & 0m0.02s &1m54.96s & - & 0m05.02s \\
  \hline
  TCRsig40 \cite{Klamt06} & 156 & $2^{73}$ & process & - & \todo{XX} & out & out & 0m05.02s \\
  \hline
\end{tabular}
\caption{Compared performances of Rocca et al. method, \textsc{libddd}, \textsc{GINsim} and our new method developped in ASP. For each test we find the name of the model, the number of its processes and its states then the target(s). The target can be a network state (set of processes) or one or some processes. "out" marks an execution asking too much time or memory and "-" marks that is not possible to do the test.
}
\end{figure}
\end{center}
This table prensents the comparisons run for 4 dynamic analysis methods applied to examples of biological regulatory networks. The models of these networks where chosen as being representative of different scales, large networks and small networks.
This table shows the effectiveness of our method compared to existing. In fact we develop in the sequel that our method provides more compared to other

@@

We developped new methods for the dynamic properties, 
identifying stable states and finding all possible paths to reach states. Comparing with other methods (Rocca's method, \textsc{GINsim} and \textsc{libddd}) is relatively faster and also permit to edit larger networks (about $2^{73}$ states) but we had also some inconclusif cases. In fact the program is inconclusif if the state is not reachable and there is some loops in the graph so the program may turn indefinitely in one of these loops since it is not possible to achieve the goals or to stop the calculation. We then proposed in this case to limit the increment to a maximum number that can be reached in the case of an endless loop and which may not be in the case where the targets are verified.
\begin{tabbing}
 \texttt{ iClingo find\_path.lp <network\_name>.lp --imax=n}
\end{tabbing}
Should be given some interesting values for this integer \texttt{"n"}, which sets the maximum number of steps. For example, the total number of states is a maximum (it will never be exceeded by a minimum path). However, it can reduce the number of sorts if it is assumed that one type will be changed by step (which is often the case of Boolean networks) or the number of shares with the same assumption.
Note that if in a way the goal is reached after a time \texttt{"n"}, the calculation stops and displays this path as a solution.

### 2015-01-08 fixPoint.tex
mise à jour

The study of fixed points (or basins of attraction) provides an important understanding of the different behaviors of a BRN (Biological Regulatory Network) \cite{wuensche1998genomic}.  
The fixed point is a stable state of the BRN in wich it is not possible any more to have new changes.
Let $(\Sigma, L, H)$ be a Process Hitting .
 It has been shown that a state $s \in L$ is a fixed point of the Process Hitting if and only if $s$ is has no next state \cite{pauleve2011modelisation} i.e. there is no playable action at this state. In fact a steady state od a Process Hitting network is a set of processes with exactly one process of each sort as well as every process has no hit with the other selected ones (process with self-hit cannot be apart of a stable state).

\subsection{Process Hitting network traduction }
In order to handle a PH biological network, it was necessary first to present it with ASP. To do this we chose the predicates: $sort$, $process$ and $action$. Below is an example of PH network shown in ASP.

\begin{example*} [Example PH network with ASP]
If we try to present the network of Figure \ref{fig:ph} we will have:
\begin{lstlisting}
sort("a"). sort("b"). sort("z"). %\label{ASPsort}
process("a", 0..1). process("b", 0..1). process("z", 0..2). %\label{ASPprocess}
action("a",0,"b",1,0). action("a",1,"a",1,0). action("b",1,"z",0,2). %\label{actions1}
action("b",0,"z",1,2). action("z",0,"a",0,1). %\label{actions2}
\end{lstlisting}
Line \ref{ASPsort} shows every sort of network with the predicate comes out and in parentheses the name of the sort. In line \ref{ASPprocess} there is a list of processes corresponding to each $sort$ for example the sort "$z$" has 3 process numbered from 0 to 2, this numbering is provided by the $2^{nd}$ parameter of the predicate $process("z", 0..2)$. Finally we find all network actions that are defined in lines \ref{actions1} and \ref{actions2}, for example the first action $action("a",0,"b",1,0)$ is an action from $a_0$ to $b_1$ to bound so $b$ from $b_1$ into $b_0$.
\end{example*}

\subsection{Search of fixed points }
Parler du point fixe et ses interrêts. \\
Decrire la nouvelle méthode qui permettent de determiner les états stables d'un réseau

In fact we have to translate the definition of a stable state in a method developped in ASP. So first we eliminate all processes with self-hit and we save them in the predicate "$shownProcess$":
\begin{lstlisting}
hiddenProcess(A,I) :-  action(A,I,B,J,K), A=B, process(A,I),process(B,J),
                       process(B,K). %\label{hiddenProcess}
shownProcess(A,I) :-  not hiddenProcess(A,I), process(A,I). %\label{shownProcess}
\end{lstlisting}
Then we have to browse this graph and extract all possible combinations of shown processes by choosing a process from each sort.
\begin{lstlisting}
1 { selectProcess(A,I) : showProcess(A,I) } 1 :- sort(A).
\end{lstlisting}
It now remains to check each combination of processes whether it is a fix point. For this we use a special type of ASP rules: a \textbf{constraint}. The idea of constraints is based on the fact that a solution would be eliminated if it does not satisfy the constraint. For our problem a combination is eliminated if there is an action between two of the selected process:
\begin{lstlisting}
:- hit(A,I,B,J), selectProcess(A, I), selectProcess(B, J), A!= B. %\label{contraintFix}
\end{lstlisting}

\begin{example}
Considering the last graphical presentation of a precess hitting \pref{fig:ph}, there are 3 sorts $a$, $b$ have 2 levels and $z$ has 3 so we can find $2*2*3 = 12$ states (whatever they can be reached or not). If we verify wether there exist fixed points we deduce that we have only one: $<b\_0, z\_2, a\_0>$. It is clear in \pref{fig:ph} that there is no action between each two processes. Besides our new ASP method proof this and returns also the same answer:
\begin{tabbing}
 \texttt{
 Answer 1 : fixProcess(a, 0), fixProcess(b, 0), fixProcess(z, 2)
 }
\end{tabbing}
\end{example}

>>>>

The study of fix points (or basins of attraction) provides an important understanding of the different behaviors of a BRN (Biological Regulatory Network) \cite{wuensche1998genomic}.  
The fixed point is a stable state of the BRN in wich it is not possible any more to have new changes.
Let $(\Sigma, L, H)$ be a Process Hitting .
 It has been shown that a state $s \in L$ is a fixed point of the Process Hitting if and only if $s$ is has no next state \cite{pauleve2011modelisation} i.e. there is no playable action at this state. In fact a steady state od a Process Hitting network is a set of processes with exactly one process of each sort as well as every process has no hit with the other selected ones (process with self-hit cannot be apart of a stable state).

\subsection{Process Hitting network traduction }
In order to handle a PH biological network, it was necessary first to present it with ASP. To do this we chose the predicates: \texttt{sort}, \texttt{process} and \texttt{action}. Below is an example of PH network written in ASP.

\begin{example*} [Example PH network with ASP]
If we try to present the network of Figure \ref{fig:ph} we will have:
\begin{lstlisting}
sort("a"). sort("b"). sort("z"). %\label{ASPsort}
process("a", 0..1). process("b", 0..1). process("z", 0..2). %\label{ASPprocess}
action("a",0,"b",1,0). action("a",1,"a",1,0). action("b",1,"z",0,2). %\label{actions1}
action("b",0,"z",1,2). action("z",0,"a",0,1). %\label{actions2}
\end{lstlisting}
Line \ref{ASPsort} shows every sort of network with the predicate comes out and in parentheses the name of the sort. In line \ref{ASPprocess} there is a list of processes corresponding to each \texttt{sort}, for example the sort \texttt{"z"} has 3 processes numbered from \texttt{0} to \texttt{2}, this numbering is provided by the $2^{nd}$ parameter of the predicate \texttt{process("z", 0..2)}. Finally we find all network actions that are defined in lines \ref{actions1} and \ref{actions2}, for example the first action \texttt{action("a",0,"b",1,0)} is an action from $a_0$ to $b_1$ to bound so $b$ from $b_1$ into $b_0$.
\end{example*}

\subsection{Search of fix points }
\todo{ Parler du point fixe et ses interrêts. \\
Décrire la nouvelle méthode qui permet de déterminer les états stables d'un réseau }

In fact we have to translate the definition of a stable state in a method developped in ASP. So first we eliminate all processes with self-hit and we save them in the predicate \texttt{shownProcess}:
\begin{lstlisting}
hiddenProcess(A,I) :-  action(A,I,B,J,K), A=B, process(A,I),process(B,J),
                       process(B,K). %\label{hiddenProcess}
shownProcess(A,I) :-  not hiddenProcess(A,I), process(A,I). %\label{shownProcess}
\end{lstlisting}
Then we have to browse this graph and extract all possible combinations of shown processes by choosing a process from each sort.
\begin{lstlisting}
1 { selectProcess(A,I) : showProcess(A,I) } 1 :- sort(A).
\end{lstlisting}
It now remains to check each combination of processes whether it is a fix point. For this we use a special type of ASP rules: a \textbf{constraint}. The idea of constraints is based on the fact that a solution would be eliminated if it does not satisfy the constraint. For our problem a combination is eliminated if there is an action between two of the selected process:
\begin{lstlisting}
:- hit(A,I,B,J), selectProcess(A, I), selectProcess(B, J), A!= B. %\label{contraintFix}
\end{lstlisting}

\begin{example}
Considering the last graphical presentation of a precess hitting \pref{fig:ph}, there are 3 sorts \texttt{"a"}, \texttt{"b"} have 2 levels and \texttt{"z"} has 3, so we can find $2*2*3 = 12$ states (whatever they can be reached or not). If we verify wether there exist fixed points we deduce that we have only one: $<b\_0, z\_2, a\_0>$. It is clear in \pref{fig:ph} that there is no action between each two processes. Besides our new ASP method proof this and returns also the same answer:
\begin{tabbing}
 \texttt{
 Answer 1 : fixProcess(a, 0), fixProcess(b, 0), fixProcess(z, 2)
 }
\end{tabbing}
\end{example}

### 2015-01-08 reachability.tex
mise à jour

\subsection{Future states identification }
From an initial known state, a PH network can evolve into several new states after a few steps. The predicate $"time (0 .. n)"$ sets the number of steps we want to play. For example if the biologist wants to know which states are reachable after 10 stages, it has only to replace $n$ by 10, and he will have $"time (0 .. 10)"$. To compute the future states it is necessary to define an initial state of the network. So for initializing the active processes we add in the ASP script representing the PH network the following rule for each sort. We note that this rules are generated automatically at the time of translating PH network to ASP and by default the level of all active processes is $0$.\\
\begin{lstlisting}
init(activeProcess("a",0)).
\end{lstlisting}
with $a$ is the name of the sort and $0$ the index of the active process.\\
The dynamic of a network is realised thanks to its actions. So to identify the future states we should start by identifying the playable actions for each state. We recall that an action is playable when both precesses: hitter and taget are active (Definition \ref{def:playableAction}). In ASP the predicate $"playableAction(A,I,B,J,K,T)"$ it is true when the processes $(A,I)$ and $(B,J)$ are active at the step $T$.
Our approch is to study the asynchronous dynamic so only one action is playable at the same step ($T$). That's why between two successive states there will be one change of one sort. We present this by the predicate $"activeFromTo(B,J,K,T)"$. It means that in the sort $B$ the active process change from index $J$ to $K$ at time step $T$.
At the same step we can find many possible changes , that's why the rule (line \ref{e2}) offers a set of all these possible changes thanks to braces.
In fact the rule is encoded with a count atom at its head, which makes it a choice rule. Rule in line \ref{e3} filters any answer with more than 1 change at the same time $T$ to ensure the asynchronous evolution.
\begin{lstlisting}
{activeFromTo(B,J,K,T)} :-  playableAction(A,I,B,J,K,T),
          instate(activeProcess(A,I),T), instate(activeProcess(B,J),T),
          J!=K, time(T). %\label{e2}
:- 2{ activeFromTo(B,J,K,T)}, time(T). %\label{e3}
\end{lstlisting}

In order to determinate the next active processes at $T+1$ we use the following rules :
\begin{lstlisting}
instate(activeProcess(B,K),T+1) :-  activeFromTo(B,J,K,T), time(T). %\label{e4}
instate(activeProcess(A,I),T+1) :-  instate(activeProcess(A,I),T),
          activeFromTo(B,J,K,T), A!=B, time(T). %\label{e5}
\end{lstlisting}

At the next step $T+1$ we find the new active process resulted from the predicate $activeFromTo$ (line \ref{e4}) as well as all the unchanged processes that correspond to the other sorts (line \ref{e5}).\\
As a result it will be displayed all possible evolutions of the netwoks.
\subsection{Reachability verification}
In this section, we focus on the reachability of a process which corresponds to the question \cite{def:reachability} :\\
“Is it possible, starting from a given initial state, to play a number of actions so that a given processes are active in the resulting state?”

\noindent Now we try to adapt the code of network evolution to resolve the reachability problem. First we define a predicate for the objective processes we call it $"goal"$, we add a rule with this predicate to the script defining the PH :
\begin{lstlisting}
goal(activeProcess("a",1)). %\label{c1}
\end{lstlisting}
The rule line \ref{c1} verifies if after the network evolution, its state satisfies the goals at step $T$. Else the answer will be eliminated.
\begin{lstlisting}
satisfiable(F,T) :-  goal(F), instate(F,T). %\label{c2}
\end{lstlisting}
The limitation of this method is that the user has to choose the number of steps of the evolution. It is an disadvantage because a search in N steps will find no solution if the shortest path to solve the rechability requires N+1 steps. The solution is to use the incremental computation mode ( \textsc{iclingo} \cite{gebser2008user}).
So we have almost the same program expect for incremental step numbers. In each step t, the program computes the playable actions $playableAction(A,I,B,J,K,t)$,the possible change $activeFromTo(B,J,K,t-1)$ and the new active processes for the next step $instate(activeProcess(A,I),t+1)$. Regarding the part of local steps we use a special constraint (rule \textbf{c4}) that means that the program should continue to the next step if it's not satisfiable so that we eliminate responses that do not meet the goals.
\begin{lstlisting}
notSatisfiable(t) :-  goal(F), not instate(F,t). %\label{c3}
:- notSatisfiable(t). %\label{c4}
\end{lstlisting}

>>>>

\subsection{Future states identification }
From an initial known state, a PH network can evolve into several new states after a few steps. The predicate \texttt{"time (0 .. n)"} sets the number of steps we want to play. For example if the biologist wants to know which states are reachable after 10 stages, it has only to replace \texttt{"n"} by 10, and he will have \texttt{"time (0 .. 10)"}. To compute the future states it is necessary to define an initial state of the network. So for initializing the active processes we add in the ASP script representing the PH network the following rule for each sort. We note that this rules are generated automatically at the time of translating PH network to ASP and by default the level of all active processes is $0$.\\
\begin{lstlisting}
init(activeProcess("a",0)).
\end{lstlisting}
with \texttt{"a"} is the name of the sort and\texttt{"0"} the index of the active process.\\
The dynamic of a network is realised thanks to its actions. So to identify the future states we should start by identifying the playable actions for each state. We recall that an action is playable when both precesses: hitter and taget are active (Definition \ref{def:playableAction}). In ASP the predicate \texttt{"playableAction(A,I,B,J,K,T)"} it is true when the processes \texttt{(A,I)} and \texttt{(B,J)} are active at the step \texttt{T}.
Our approch is to study the asynchronous dynamic so only one action is playable at the same step ( \texttt{T}). That's why between two successive states there will be one change of one sort. We present this by the predicate  \texttt{"activeFromTo(B,J,K,T)"}. It means that in the sort \texttt{B} the active process change from index \texttt{J} to \texttt{K} at time step \texttt{T}.
At the same step we can find many possible changes , that's why the rule (line \ref{e2}) offers a set of all these possible changes thanks to braces.
In fact the rule is encoded with a count atom at its head, which makes it a choice rule. Rule in line \ref{e3} filters any answer with more than 1 change at the same time \texttt{T} to ensure the asynchronous evolution.
\begin{lstlisting}
{activeFromTo(B,J,K,T)} :-  playableAction(A,I,B,J,K,T),
          instate(activeProcess(A,I),T), instate(activeProcess(B,J),T),
          J!=K, time(T). %\label{e2}
:- 2{ activeFromTo(B,J,K,T)}, time(T). %\label{e3}
\end{lstlisting}

In order to determinate the next active processes at \texttt{T+1} we use the following rules :
\begin{lstlisting}
instate(activeProcess(B,K),T+1) :-  activeFromTo(B,J,K,T), time(T). %\label{e4}
instate(activeProcess(A,I),T+1) :-  instate(activeProcess(A,I),T),
          activeFromTo(B,J,K,T), A!=B, time(T). %\label{e5}
\end{lstlisting}

At the next step \texttt{T+1} we find the new active process resulted from the predicate \texttt{activeFromTo} (line \ref{e4}) as well as all the unchanged processes that correspond to the other sorts (line \ref{e5}).\\
As a result it will be displayed all possible evolutions of the netwoks.
\subsection{Reachability verification}
In this section, we focus on the reachability of a process which corresponds to the question \ref{def:reachability} :\\
“Is it possible, starting from a given initial state, to play a number of actions so that a given processes are active in the resulting state?”

\noindent Now we try to adapt the code of network evolution to resolve the reachability problem. First we define a predicate for the objective processes we call it \texttt{"goal"}, we add a rule with this predicate to the script defining the PH :
\begin{lstlisting}
goal(activeProcess("a",1)). %\label{c1}
\end{lstlisting}
The rule line \ref{c1} verifies if after the network evolution, its state satisfies the goals at step \texttt{T}. Else the answer will be eliminated.
\begin{lstlisting}
satisfiable(F,T) :-  goal(F), instate(F,T). %\label{c2}
\end{lstlisting}
The limitation of this method is that the user has to choose the number of steps of the evolution. It is an disadvantage because a search in N steps will find no solution if the shortest path to solve the rechability requires N+1 steps. The solution is to use the incremental computation mode ( \textsc{iclingo} \cite{gebser2008user}).
So we have almost the same program expect for incremental step numbers. In each step t, the program computes the playable actions \texttt{playableAction(A,I,B,J,K,t)},the possible change \texttt{activeFromTo(B,J,K,t-1)} and the new active processes for the next step \texttt{instate(activeProcess(A,I),t+1)}. Regarding the part of local steps we use a special constraint (rule \textbf{c4}) that means that the program should continue to the next step if it's not satisfiable so that we eliminate responses that do not meet the goals.
\begin{lstlisting}
notSatisfiable(t) :-  goal(F), not instate(F,t). %\label{c3}
:- notSatisfiable(t). %\label{c4}
\end{lstlisting}
